Issues with Dynamical Measurements Across the Disk

### 2019-02-15 paper/ms.tex
Various small fixes to Discussion

To explore the magnitude of this effect, we consider the following program.
First, we assume a cluster mass $m_c$ and estimate the expected action-space
dispersion from Equation~\ref{eq:action_disp}. We then consult
Figure~\ref{fig:many_orbit_wrong_ref} to determine the $z$ offset necessary in
order for the induced error in the vertical action to be the same as the
expected action-space dispersion. If this were the case, an observer would
have to account for the different midplane of the field star and the cluster.
We repeat this analysis for each of the three orbits considered in
Section~\ref{ssec:quant}.

With a characteristic $z$ offset in hand, we consult
Figure~\ref{fig:range_deltaphi} to convert this $z$ offset into a $\Delta
\phi$, which we convert to an arclength or characteristic distance (the
difference between the two will be negligible for the small $\Delta \phi$'s we
will compute). Therefore, if an observer is attempting to reconstruct a
cluster with a given mass on a given orbit, we will give a characteristic
distance between a field star and the cluster within which an observer might
not need to consider differences in their respective local midplanes.

@@

We now convert the $z$~offset-$m_c$ relation to an $R_{\n}$-$m_c$ relation,
where $R_{\n}$ indicates a sort of ``solar neighborhood'' radius. An observer
attempting to reconstruct an open cluster of mass $m_c$ with perfect knowledge
of the midplane at the location of the cluster would expect to find the
ejected members using a dynamical cut for field stars within a distance
$R_{\n}$ of the cluster. If such an observer wants to find ejected stars that
are at a distance greater than $R_{\n}$, a more sophisticated analysis would
be required, the details of which are not apparent to the authors of this
work.

We use the relation in Figure~\ref{fig:range_deltaphi}, which shows the
typical $z$ offset at each $\Delta \phi$, to convert a given $z$ offset into a
$\Delta\phi$, which we then convert into a chord length which we interpret as
$R_{\n}$, the neighborhood around the cluster. If the $z$~offset is greater
than the maximum range value of the galaxy, we simply report the maximum chord
length ($2\times8.2\,\kpc$). The result of this procedure is shown in
Figure~\ref{fig:Rn_mc}. The solid lines indicate the neighborhood values
assuming the mean relation between $z$~offset and $m_c$, and the dashed lines
show the $+1\,\sigma$ and $-1\,\sigma$ relations, indicative of the strong
$\phi$-dependence of the midplane effect.

@@

\acknowledgments
We would like to thank Megan Bedell, David W. Hogg, and Kathryn Johnston for
many useful discussions. A.B. would like to thank Todd Phillips for helpful
discussions. A.B. was supported in part by the Roy \& Diana Vagelos Program in
the Molecular Life Sciences and the Roy \& Diana Vagelos Challenge Award. The
work of \Gus{everyone} is supported by the Simons Foundation.

>>>>

To explore the magnitude of this effect, we consider the following program.
First, we assume a cluster mass $m_c$ and estimate the expected action-space
dispersion from Equation~\ref{eq:action_disp}. We then consult
Figure~\ref{fig:many_orbit_wrong_ref} to determine the $z$ offset necessary in
order for the induced error in the vertical action to be the same as the
expected action-space dispersion. If this were the case, an observer would
have to account for the different midplane of the field star and the cluster.
We perform this analysis for the thin-disk and thick-disk orbits considered in
Section~\ref{ssec:quant}, since the halo orbit is unrealistic for known open
clusters (Table~\ref{tab:real_clusters}).

With a characteristic $z$ offset in hand, we consult
Figure~\ref{fig:range_deltaphi} to convert this $z$ offset into a $\Delta
\phi$, which we convert to an arclength or characteristic distance, which we
refer to as the ``neighborhood radius'' or $R_{\n}$. Therefore, if an observer
is attempting to reconstruct a cluster with a given mass on a given orbit, we
will give a characteristic distance between a field star and the cluster
within which an observer might not need to consider differences in their
respective local midplanes.

@@

We now convert the $z$~offset-$m_c$ relation to an $R_{\n}$-$m_c$ relation,
where $R_{\n}$ indicates the neighborhood radius. An observer
attempting to reconstruct an open cluster of mass $m_c$ with perfect knowledge
of the midplane at the location of the cluster would expect to find the
ejected members using a dynamical cut for field stars within a distance
$R_{\n}$ of the cluster. If such an observer wants to find ejected stars that
are at a distance greater than $R_{\n}$, a more sophisticated analysis would
be required.

We use the relation in Figure~\ref{fig:range_deltaphi}, which shows the
typical $z$ offset at each $\Delta \phi$, to convert a given $z$~offset into a
typical $\Delta\phi$. We then convert this $\Delta \phi$ into a chord length
(see Figure~\ref{fig:fig_to_explain}) which we interpret as $R_{\n}$, the
neighborhood around the cluster. If the $z$~offset is greater than the maximum
range value of the galaxy, we simply report the maximum chord length
($2\times8.2\,\kpc$). The result of this procedure is shown in
Figure~\ref{fig:Rn_mc}. The solid lines indicate the neighborhood values
assuming the mean relation between $z$~offset and $m_c$, and the dashed lines
show the $+1\,\sigma$ and $-1\,\sigma$ relations, indicative of the strong
$\phi$-dependence of the midplane effect.

@@

\acknowledgments
We would like to thank Megan Bedell, Tobias Buck, David W. Hogg, and Kathryn
Johnston for many useful discussions. A.B. would like to thank Todd Phillips
for helpful discussions. A.B. was supported in part by the Roy \& Diana
Vagelos Program in the Molecular Life Sciences and the Roy \& Diana Vagelos
Challenge Award. The work of \Gus{everyone} is supported by the Simons
Foundation. \Gus{remove last sentence if everyone CCA affiliated}
